Open Peer Review

### 2019-10-11 manuscript.Rmd
update code and download pdf files

---
title: "Open Peer Review"
author: "Daniel Lakens"
date: "22-9-2019"
output: html_document
---

@@

TRS_data_sorted <- TRS_data[ with( TRS_data , order ( df_link)),]

@@

>>>>

---
title: "Open Peer Review"
author: "Daniel Lakens"
date: "22-9-2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

#TRS_data_sorted <- TRS_data[ with( TRS_data , order ( df_link)),]

#Create dataframe for TRS and PeerJ of unique rows (e.g., for days)
TRS_unique <- TRS_data[!duplicated(TRS_data$df_link),]
PeerJ_unique <- PeerJ_data[!duplicated(PeerJ_data$df_link),]

# One submission to PeerJ was accepted but no reviewer info. It means they are accepted by the editor? Or just an early mistake.
sum(is.na(PeerJ_unique$df_days))

# Mean review time (almost the same as Nino original - we have a few more pdf's)
TRS_mean_review_time <- mean(TRS_unique$df_days)
PeerJ_mean_review_time <- mean(PeerJ_unique$df_days, na.rm = TRUE)

# How many reviews are masked?
mean(TRS_data$df_masked)
mean(PeerJ_data$df_masked)

length(TRS_data$df_link)
length(PeerJ_data$df_link)

# Exploratory
# Randomly split masked over 100 subgroups to see progression over time - seems stable.
df_over_time <- data.frame(TRS_data$df_masked[1:3600], rep(seq(1,100,1),each = 360))
colnames(df_over_time) <- c("masked", "time") # specify columns names
x <- group_by(df_over_time, time)
x <- summarize(x, m = mean(masked))

df_over_time <- data.frame(PeerJ_data$df_masked[1:12300], rep(seq(1,100,1),each = 1230))
colnames(df_over_time) <- c("masked", "time") # specify columns names
x <- group_by(df_over_time, time)
x <- summarize(x, m = mean(masked))

@@

In Nino's BEP there were  3552 reviews in RSOS. I have 3629 after running all his code.
